Investigating Fault-Proneness Through Hotfix Commits:\\A Research in the Light of Different Programming Languages

### 2016-02-17 msr_paper/main.tex
Moved files used for MSR paper into the msr_paper folder

\section{Related Work}
Many researchers have explored various aspects of defects in software through the use of versioning system history logs. We have also decided to follow this approach due to its openness and accessibility. This method is also very widely adopted amongst the MSR community \cite{Hattori2008}. Our investigation focused primarily on two research aspects and involved exploring existing work related to: 1) identifying hotfix commits and 2) comparison of programming languages’ stability.

\subsection{Identifying hotfix commits}
The first major problem we had to solve was identifying actual hotfix commits. Due to Boa’s limitations, we were not able to find commit history from hotfix branch. We were only capable of collecting information with regard to commits performed on the main branch. Therefore, we reviewed various papers to identify the most appropriate method of determining the type of the commit to extract only the ones related to a bug correction.\par

@@

In terms of the time aspect, there was another paper which investigated the duration between the moment when a change is applied to a specific branch and the moment the new code was merged into the trunk \cite{Williams2008}. However, they explored branches in general without focusing specifically on bugfix branches. Some other scientists were trying to explain people’s behaviour during commits by investigating their commit frequency distribution. As a result, they discovered that on average the time between commits was 3.206 days and half of all the contributors spent less than 13.78 hours between 50\% of their commits \cite{Kolassa2013}.\par

@@

\subsection{Overall performance of programming languages}
We started with investigating the overall reliability of different languages regardless of the topic they belonged to.\\
\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{Bar_chart}
\caption{Overall hotfixes per programming languages for 100 releases.}
\label{fig:my_label}
\end{figure}

@@

Java is the most reliable language by far according to our results. C, C++ and Python have quite similar hotfix rates. Java is a strongly-typed language which has a definitive advantage over the others. Thus, we can say this aspect of our hypothesis is somewhat supported. It’s only partially justified because while Python, C and C++ have similar hotfix rates, Python still ranks at the bottom of our results table.\\

@@

\section{Conclusions and Future Work}
We have presented a research in detecting the fault-proneness of programming languages through hotfix commits - a topic that has not been investigated so far. To increase the significance of our study we performed both an overall estimation of hotfixes and a topic-specific analysis. The tool that we created was written in Boa and mined repositories from SourceForge 2013’s dataset. Our goal was to verify whether the general relationships between languages’ reliability holds with regard to hotfixes. Specifically, we investigated the following relations: strongly-typed vs weakly-typed languages, static vs dynamic and functional vs procedural. We expected that in each pair the first group of languages will be dominant. Although our overall results supported our hypothesis, on a topic-by-topic basis we were not able to verify it.\par
Therefore, we believe that some future work has to be accomplished to increase the validity of our observations. In particular, more datasets could be used, including Github (provided that projects are categorised into topics). Further improvements may be done to identify bump commits more accurately. Recently, a few commercial projects have been open-sourced and as a result, we could use them to enhance the quality of our data. In such projects, releases will have occurred more frequently and thus, there is a higher probability of identifying more hotfixes.\par
Finally, we believe that our paper provides a good foundation for future research to be done in this topic. We expect that the results we obtained will help developers and project managers improve their planning and understand what the most appropriate languages are for their specific topic.

>>>>

\section{Related Work}
Many researchers have explored various aspects of defects in software through the use of versioning system history logs. We have also decided to follow this approach due to its openness and accessibility. This method is also very widely adopted amongst the MSR community \cite{Hattori2008}. Our investigation focused primarily on two research aspects and involved exploring existing work related to: 1) identifying hotfix commits and 2) comparison of programming languages' stability.

\subsection{Identifying hotfix commits}
The first major problem we had to solve was identifying actual hotfix commits. Due to Boa's limitations, we were not able to find commit history from hotfix branch. We were only capable of collecting information with regard to commits performed on the main branch. Therefore, we reviewed various papers to identify the most appropriate method of determining the type of the commit to extract only the ones related to a bug correction.\par

@@

In terms of the time aspect, there was another paper which investigated the duration between the moment when a change is applied to a specific branch and the moment the new code was merged into the trunk \cite{Williams2008}. However, they explored branches in general without focusing specifically on bugfix branches. Some other scientists were trying to explain people's behaviour during commits by investigating their commit frequency distribution. As a result, they discovered that on average the time between commits was 3.206 days and half of all the contributors spent less than 13.78 hours between 50\% of their commits \cite{Kolassa2013}.\par

@@

\subsection{Overall performance of programming languages}
We started with investigating the overall reliability of different languages regardless of the topic they belonged to.\\
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{Bar_chart}
\caption{Overall hotfixes per programming languages for 100 releases.}
\label{fig:my_label}
\end{figure}

@@

Java is the most reliable language by far according to our results. C, C++ and Python have quite similar hotfix rates. Java is a strongly-typed language which has a definitive advantage over the others. Thus, we can say this aspect of our hypothesis is somewhat supported. It's only partially justified because while Python, C and C++ have similar hotfix rates, Python still ranks at the bottom of our results table.\\

@@

\section{Conclusions and Future Work}
We have presented a research in detecting the fault-proneness of programming languages through hotfix commits - a topic that has not been investigated so far. To increase the significance of our study we performed both an overall estimation of hotfixes and a topic-specific analysis. The tool that we created was written in Boa and mined repositories from SourceForge 2013's dataset. Our goal was to verify whether the general relationships between languages' reliability holds with regard to hotfixes. Specifically, we investigated the following relations: strongly-typed vs weakly-typed languages, static vs dynamic and functional vs procedural. We expected that in each pair the first group of languages will be dominant. Although our overall results supported our hypothesis, on a topic-by-topic basis we were not able to verify it.\par
Therefore, we believe that some future work has to be accomplished to increase the validity of our observations. In particular, more datasets could be used, including Github (provided that projects are categorised into topics). Further improvements may be done to identify bump commits more accurately. Recently, a few commercial projects have been open-sourced and as a result, we could use them to enhance the quality of our data. In such projects, releases will have occurred more frequently and thus, there is a higher probability of identifying more hotfixes.\par
Finally, we believe that our paper provides a good foundation for future research to be done in this topic. We expect that the results we obtained will help developers and project managers improve their planning and understand what the most appropriate languages are for their specific topic.
